---
title: "AI-Generated Fake News: User Study"
output: 
  bookdown::pdf_document2: 
    {
    fig_caption: yes,
    extra_dependencies: ["dcolumn","rotating","graphicx"]
    }
    
date: "2023-06-23"
---

```{r setup, include=FALSE,echo=FALSE,massAge = FALSE}
knitr::opts_chunk$set(echo = FALSE, results = "asis")
```

```{r,echo=FALSE,include=FALSE}
library(readr)
library(tidyverse)
library(reshape2)
library(nortest)
library(sandwich)
library(lmtest)
library(zoo)
library(MASS)
library(lme4)
library(lmerTest)
library(estimatr)
library(stargazer)
library(sjPlot)
library(sjstats)
library(infotheo)
library(Hmisc)
library(parameters)
library(car)
library(AICcmodavg)
library(ROCR)
library(epitab)
library(xtable)
library(kableExtra)
library(bookdown)
library(ggstatsplot)
library(ordinal)
library(ggpubr)
library(coefplot)
library(dotwhisker)
library(ggstats)
library(performance)
library(lavaan)
library(emmeans)
library(gridExtra)
library(grid)
library(boot)
library(rstatix)
library(psych)
library(DescTools)
library(rcompanion)
library(Matrix)
library(ggsignif)
```

```{r}
# Function def
# requires ggstatsplot
SignifStar <- function(data) {
  data_stat <- extract_stats(data)
  if (data_stat$subtitle_data$p.value < 0.001) {
    annotation <- "***"
  } else if (data_stat$subtitle_data$p.value < 0.01 & data_stat$subtitle_data$p.value > 0.0001) {
    annotation <- "**"
  } else if (data_stat$subtitle_data$p.value < 0.05 & data_stat$subtitle_data$p.value > 0.001) {
    annotation <- "**"
  } else if (data_stat$subtitle_data$p.value < 0.1 & data_stat$subtitle_data$p.value > 0.05) {
    annotation <- "."
  }
}
```




```{r load,echo=FALSE,include=FALSE}
# read the processed_data
processed_data <- read_csv(file.path("Data", "processed_data.csv"))
```



```{r, echo = FALSE}
# Data processing
processed_data <- rename(processed_data, user_id = ResponseId)
processed_data <- rename(processed_data, fall_for_fake_news_status = fall_for_fake_news)
processed_data <- processed_data %>%
  dplyr::filter(WillingnessToShare != -1) %>%
  dplyr::select(user_id, Statement, WillingnessToShare) %>%
  mutate(WillingnessToShare_z = ((WillingnessToShare - mean(WillingnessToShare)) / sd(WillingnessToShare))) %>%
  full_join(processed_data %>% dplyr::select(-WillingnessToShare), by = c("user_id", "Statement")) %>%
  mutate(WillingnessToShare = replace_na(WillingnessToShare, -1))

processed_data <- processed_data %>%
  mutate(fake_news_generation_source_z = ((fake_news_generation_source - mean(fake_news_generation_source)) / sd(fake_news_generation_source))) %>%
  mutate(PerceivedVeracity_z = ((PerceivedVeracity - mean(PerceivedVeracity)) / sd(PerceivedVeracity))) %>%
  mutate(vaccination_z = ((VaccinationStatus - mean(VaccinationStatus)) / sd(VaccinationStatus))) %>%
  mutate(SocialOrientation_z = ((SocialOrientation - mean(SocialOrientation)) / sd(SocialOrientation))) %>%
  mutate(EconomicOrientation_z = ((EconomicOrientation - mean(EconomicOrientation)) / sd(EconomicOrientation))) %>%
  mutate(PoliticalOrientation_z = ((PoliticalOrientation - mean(PoliticalOrientation)) / sd(PoliticalOrientation))) %>%
  mutate(Ethnicity_z = ((Ethnicity - mean(Ethnicity)) / sd(Ethnicity))) %>%
  mutate(EthnicityBinary_z = ((EthnicityBinary - mean(EthnicityBinary)) / sd(EthnicityBinary))) %>%
  mutate(Fuency_z = ((Fluency - mean(Fluency)) / sd(Ethnicity))) %>%
  mutate(education_z = ((EducationYears - mean(EducationYears)) / sd(Fluency))) %>%
  mutate(religious_z = ((Religiosity - mean(Religiosity)) / sd(Religiosity))) %>%
  mutate(Income_z = ((Income - mean(Income)) / sd(Income))) %>%
  mutate(NewsConsumption_z = ((NewsConsumption - mean(NewsConsumption)) / sd(NewsConsumption))) %>%
  mutate(Concern_z = ((Concern - mean(Concern)) / sd(Concern))) %>%
  mutate(CRT_score_z = ((CRT - mean(CRT)) / sd(CRT))) %>%
  mutate(Time_to_respond_z = ((Time_to_respond - mean(Time_to_respond)) / sd(Time_to_respond))) %>%
  mutate(Age_z = ((Age - mean(Age)) / sd(Age))) %>%
  mutate(StatementSequence_z = ((StatementSequence - mean(StatementSequence)) / sd(StatementSequence))) %>%
  mutate(fake_news_generation_source_fac = as.factor(fake_news_generation_source)) %>%
  mutate(SocialOrientation = as.factor(SocialOrientation)) %>%
  mutate(EconomicOrientation = as.factor(EconomicOrientation)) %>%
  mutate(PoliticalOrientation = as.factor(PoliticalOrientation)) %>%
  mutate(Income = as.factor(Income)) %>%
  mutate(Fluency = as.factor(Fluency)) %>%
  mutate(Religiosity = as.factor(Religiosity)) %>%
  mutate(Ethnicity = as.factor(Ethnicity)) %>%
  mutate(Statement = as.factor(Statement)) %>%
  mutate(VaccinationStatus = as.factor(VaccinationStatus)) %>%
  mutate(fall_for_fake_news_status = as.factor(fall_for_fake_news_status)) %>%
  mutate(EthnicityBinary = as.factor(EthnicityBinary)) %>%
  mutate(statement_source = as.factor(statement_source)) %>%
  mutate(NewsConsumption = as.factor(NewsConsumption)) %>%
  mutate(GenderBinary = as.factor(GenderBinary)) %>%
  #  mutate(Veracity = as.factor(Veracity)) %>%
  mutate(WillingnessToShare_fac = as.factor(WillingnessToShare))

processed_data <- processed_data %>%
  group_by(user_id) %>%
  mutate(
    fail_for_fake_news_rate =
      sum(fall_for_fake_news_status == 1, na.rm = T) / n()
  )

processed_data <- processed_data %>%
  group_by(user_id, fake_news_generation_source) %>%
  mutate(
    fall_for_fake_news_rate_per_fake_news_generation_source =
      sum(fall_for_fake_news_status == 1, na.rm = T) / n()
  )



processed_data <- processed_data %>% dplyr::ungroup()
```




```{r, echo = FALSE}
# Create a contingency table


table_share <- table(
  processed_data %>%
    .$fake_news_generation_source,
  processed_data %>%
    .$WillingnessToShare
)
# contingency_table_share
rownames(table_share) <- c("Human-generated", "AI-generated")
colnames(table_share) <- c("Don't know", "Not share", "Share")
table_share
```
```{r, echo = FALSE}
processed_data %>%
  group_by(fake_news_generation_source) %>%
  summarise(mean_veracity = mean(PerceivedVeracity))
```


```{r img1, out.width="70%",fig.cap="\\label{fig:Veracity}Veracity distribution of fake news from 1 (strongly disagree) to 5 (strongly agree) ", fig.align='center'}
# Sample plot
# pdf("Veracity_disturb.pdf", width=8, height=4)
#

ggplot(
  data = processed_data %>% group_by(PerceivedVeracity, fake_news_generation_source_fac) %>%
    summarise(percentage = n() / length(processed_data$PerceivedVeracity)) %>%
    mutate(PerceivedVeracity = as.factor(PerceivedVeracity)),
  aes(x = PerceivedVeracity, y = percentage, fill = fake_news_generation_source_fac)
) +
  geom_bar(stat = "identity", position = position_dodge()) +
  scale_fill_manual(
    values = c("#000666", "#990000"), name = "",
    labels = c("Human-generated", "AI-generated")
  ) +
  scale_x_discrete(
    labels = c(
      "0" = "'Very inaccurate'",
      "1" = "'Somehow inaccurate'",
      "2" = "'Neutral'", "3" = "'Somehow accurate'",
      "4" = "'Very accurate'"
    )
  ) +
  ylab("Relative Frequency (in %)") +
  xlab("PerceivedVeracity") +
  theme_blank() +
  theme(
    legend.position = c(0.8, 0.9), legend.text = element_text(size = 11),
    axis.text = element_text(size = 12),
    axis.text.x = element_text(angle = 90),
    axis.title = element_text(size = 12, face = "plain")
  )


# dev.off()
```


```{r}
table_share_dataframe <- table_share %>%
  as.data.frame() %>%
  transform(Var2 = factor(Var2,
    levels = c("Not share", "Share", "Don't know")
  )) %>%
  mutate(Color = c("#000666", "#990000", "#000666", "#990000", "#000666", "#990000")) %>%
  mutate(percentage = round(Freq * 100 / (sum(Freq) / 2), 2))

# pdf("Sharing_chi.pdf", width=6, height=4)
pal_fill <- dplyr::distinct(table_share_dataframe, Var1, Color) |>
  tibble::deframe()

ggplot(table_share_dataframe, aes(Var1, percentage)) +
  geom_col(aes(fill = Var1, alpha = Var2),
    position = position_stack(reverse = TRUE)
  ) +
  geom_text(aes(label = paste0("N = ", Freq, " (", percentage, "%)"), group = Var2),
    color = "white",
    position = position_stack(vjust = 0.7, reverse = TRUE), show.legend = FALSE
  ) +
  scale_fill_manual(values = pal_fill) +
  scale_alpha_manual(values = c(1, 0.6, 0.4)) +
  guides(fill = "none", alpha = guide_legend(reverse = TRUE, title = "Level of clarity")) +
  theme_blank() +
  # theme(legend.title =  "clarity") +
  ylab("") +
  xlab("")
# dev.off()
```



```{r img2, out.width="70%",fig.cap="\\label{fig:CRT}Cognative Reflection Test scores distribution",fig.align='center'}
ggplot(
  data = processed_data %>% dplyr::select(user_id, CRT) %>% unique(),
  aes(x = as.factor(CRT))
) +
  geom_bar(alpha = 0.8, fill = "gray5") +
  labs(x = "CRT score", y = "Frequency") +
  theme_blank() +
  theme(plot.title = element_text(hjust = 0.5))
```





```{r}
gghistogram(processed_data %>% dplyr::select(user_id, Age, Gender) %>% unique(),
  x = "Age",
  add = "mean", rug = TRUE, fill = "Gender",
  xlab = "Age (years)", ylab = "Frequency",
  palette = "lancet"
)
```







```{r img3,fig.cap="\\label{fig:Gender}Participants' Gender distribution",out.width="70%",fig.align='center'}
ggplot(
  data = processed_data %>% dplyr::select(user_id, Gender) %>% unique(),
  aes(x = Gender)
) +
  geom_bar(alpha = 0.8, fill = "gray5") +
  theme_minimal() +
  labs(x = "Gender", y = "Frequency") +
  ggtitle("Gender distribution") +
  theme_blank() +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
```




```{r img4,fig.cap="\\label{fig:SocialOrientationDisp}Participants' SocialOrientation orientation (with 1 very liberal) to 5 (very conservative)",out.width="70%",fig.align='center'}
ggplot(
  data = processed_data %>% dplyr::select(user_id, SocialOrientation) %>% unique(),
  aes(x = SocialOrientation)
) +
  geom_bar(alpha = 0.8, fill = "gray5", width = 0.6) +
  scale_x_discrete(labels = c(
    "0" = "Strongly liberal", "1" = "Somewhat liberal", "2" = "Moderate",
    "3" = "Somewhat conservative", "4" = "Strongly conservative"
  )) +
  labs(x = "SocialOrientation orientation", y = "Frequency") +
  ggtitle("SocialOrientation orientation ") +
  theme_blank() +
  theme(plot.title = element_text(hjust = 0.5))
```




```{r img5,fig.cap="\\label{fig:EcDisp}Participants' EconomicOrientation orientation (with 1 very liberal) to 5 (very conservative)",out.width="70%",fig.align='center'}
ggplot(
  data = processed_data %>% dplyr::select(user_id, EconomicOrientation) %>% unique(),
  aes(x = EconomicOrientation)
) +
  geom_bar(alpha = 0.8, fill = "gray5", width = 0.6) +
  scale_x_discrete(labels = c(
    "0" = "Strongly liberal", "1" = "Somewhat liberal", "2" = "Moderate",
    "3" = "Somewhat conservative", "4" = "Strongly conservative"
  )) +
  labs(x = "EconomicOrientation orientation", y = "Frequency") +
  theme_blank() +
  theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r}
ggplot(
  data = processed_data %>% dplyr::select(user_id, PoliticalOrientation) %>% unique(),
  aes(x = PoliticalOrientation)
) +
  geom_bar(alpha = 0.8, fill = "gray5", width = 0.6) +
  scale_x_discrete(labels = c(
    "0" = "Left", "1" = "Moderate", "2" = "Right",
    "3" = "Other"
  )) +
  labs(x = "EconomicOrientation orientation", y = "Frequency") +
  theme_blank() +
  theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r, echo=FALSE}
processed_data %>%
  group_by(PoliticalOrientation) %>%
  unique() %>%
  summarise(percentage = n() * 100 / length(.$PoliticalOrientation))
```





```{r img7,fig.cap="\\label{fig:VaccDisp}Participants' Covid vaccination status",out.width="70%",fig.align='center'}
ggplot(
  data = processed_data %>% dplyr::select(user_id, VaccinationStatus) %>% unique(),
  aes(x = VaccinationStatus)
) +
  geom_bar(alpha = 0.8, fill = "gray5", width = 0.4) +
  scale_x_discrete(labels = c("0" = "Not vaccinated", "1" = "Vaccinated")) +
  labs(x = "vaccination status", y = "Frequency") +
  theme_blank() +
  theme(plot.title = element_text(hjust = 0.5))
```


```{r img8,fig.cap="\\label{fig:Check}Frequency distribution of checking Covid news from 1 (never) to 5 (very often)",out.width="70%",fig.align='center'}
ggplot(
  data = processed_data %>%
    mutate(NewsConsumption = as.factor(NewsConsumption)) %>%
    dplyr::select(user_id, NewsConsumption) %>% unique(),
  aes(x = NewsConsumption)
) +
  geom_bar(alpha = 0.8, fill = "gray5") +
  scale_x_discrete(labels = c(
    "0" = "Never", "1" = "Rarely", "2" = "Sometimes",
    "3" = "Often", "4" = "Very often"
  )) +
  labs(x = "Level of checking Covid news proactively", y = "Frequency") +
  theme_blank() +
  theme(plot.title = element_text(hjust = 0.5))
```

# RQ 1



```{r,echo=FALSE}
# Test whether the veracity of human-generated fake news is normal distribution

accuracyNormalityTestHuman <- lillie.test(
  processed_data %>% dplyr::filter(fake_news_generation_source == 0) %>%
    .$PerceivedVeracity
)

# print the result
print(accuracyNormalityTestHuman)
```


```{r, echo = FALSE}
# Test whether the veracity of AI-generated fake news is normal distribution

accuracy_normality_test_AI <- lillie.test(
  filter(processed_data, fake_news_generation_source == 1) %>%
    .$PerceivedVeracity
)

# print the result
print(accuracy_normality_test_AI)
```

As the groups are not normal and the values are ordinal, we use *Mann Whitney U Test*. As the *p-value* is less than 0.05, we can conclude that these two groups are not from the same distribution.

```{r, echo=FALSE}
# final result of Wilcox test

hypothesis_accuracy <- wilcox.test(
  filter(processed_data, fake_news_generation_source == 0) %>%
    .$PerceivedVeracity,
  filter(processed_data, fake_news_generation_source == 1) %>%
    .$PerceivedVeracity,
  conf.int = TRUE
)

hypothesis_accuracy
```


# RQ 2

Before testing *Hypothesis B*, pre-processing on the data is essential. As in the survey regarding willingness to share has three options (*Yes*,*Don't know*,*No*), first, w,e should drop all the responses with *'Don't know'*. Dropping the *Don't know* option makes our variable binary. Eliminating the *Don't know* option resulted in an 18.75 reduction in data. We use the *Ch-square test* to check if the proportion of binary variables are the same in both groups. 


The contingency table of our data is as follow.

```{r, echo = FALSE}
# Create a contingency table


contingency_table_share <- table(
  processed_data %>% dplyr::filter(WillingnessToShare != -1) %>%
    .$fake_news_generation_source,
  processed_data %>% dplyr::filter(WillingnessToShare != -1) %>%
    .$WillingnessToShare
)
# contingency_table_share
rownames(contingency_table_share) <- c("Human-generated", "AI-generated")
colnames(contingency_table_share) <- c("Not share", "Share")
contingency_table_share
```


```{r}
# Perform the chi-square test
result_Chi_share <- chisq.test(contingency_table_share)

# Print the result
print(result_Chi_share)
```




```{r}
pdf("Average_faliure_rate.pdf", width = 7, height = 5)
average_faliure_rate <- ggwithinstats(
  data = processed_data %>%
    group_by(user_id, fake_news_generation_source) %>%
    dplyr::summarize(mean_failure_rate = mean(fall_for_fake_news_rate_per_fake_news_generation_source) * 100, .groups = "drop"),
  pairwise.comparisons = TRUE,
  x = fake_news_generation_source,
  y = mean_failure_rate,
  xlab = "",
  ylab = "Subjects' average failure rate in evaluating fake news veracity (in %)",
  k = 3L,
  type = "p",
  conf.level = 0.95,
  results.subtitle = TRUE,
  point.args = list(alpha = 0),
  centrality.point.args = list(color = c("#000666", "#990000")),
  centrality.label.args = list(
    size = 3.5, nudge_x = 0.4, segment.linetype = 4,
    min.segment.length = 0
  ),
  centrality.path = FALSE,
  point.path = FALSE,
  ggplot.component = list(aes(fill = fake_news_generation_source))
)

average_faliure_rate +
  scale_fill_manual(values = c("#000666", "#990000")) +
  scale_x_discrete(labels = c("Human-generated fake news", "AI-generated fake news")) +
  theme(
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 10, face = "plain")
  ) +
  geom_signif(
    y_position = c(105), xmin = c(1), xmax = c(2),
    annotation = SignifStar(average_faliure_rate), tip_length = 0
  )

dev.off()
```





```{r}
pdf("Time_disturb.pdf", width = 7, height = 5)

time_disturb <- ggwithinstats(
  data = processed_data %>%
    group_by(user_id, fake_news_generation_source) %>%
    dplyr::summarize(mean_response_time = mean(Time_to_respond), .groups = "drop") %>%
    dplyr::filter(mean_response_time <= quantile(.$mean_response_time, 0.9)),
  x = fake_news_generation_source,
  y = mean_response_time,
  pairwise.comparisons = TRUE,
  type = "p",
  xlab = "",
  ylab = "Average response time (in s) at subject-level",
  results.subtitle = TRUE,
  pairwise.display = "significant",
  point.path = FALSE,
  point.args = list(alpha = 0),
  centrality.point.args = list(color = c("#000666", "#990000")),
  centrality.label.args = list(size = 3.5, nudge_x = 0.4, segment.linetype = 4, min.segment.length = 0),
  centrality.path = FALSE,
  violin.args = list(width = 0.5, alpha = 0.2, na.rm = TRUE),
  k = 3L,
)

time_disturb +
  scale_fill_manual(values = c("#000666", "#990000")) +
  scale_x_discrete(labels = c("Human-generated fake news", "AI-generated fake news")) +
  geom_signif(
    y_position = c(12), xmin = c(1), xmax = c(2),
    annotation = SignifStar(time_disturb), tip_length = 0
  )
dev.off()
```


# Regressions:

The detail sets of variable and the equation is avalibale at the body of the paper. 








```{r, echo=FALSE}
# Run Regression

PerceivedVeracity_linear <- lmer(
  PerceivedVeracity_z ~ fake_news_generation_source + VaccinationStatus +
    NewsConsumption_z + Concern_z + CRT_score_z +
    StatementSequence_z +
    PoliticalOrientation + EconomicOrientation + Income_z + Religiosity + EthnicityBinary +
    education_z + Age_z + GenderBinary + (1 | user_id),
  data = processed_data %>% dplyr::filter(
    PoliticalOrientation != 3,
    GenderBinary != -1
  )
)
# summary(PerceivedVeracity_linear)


# vif(PerceivedVeracity_linear)


PerceivedVeracity_linear_AI <- lmer(
  PerceivedVeracity_z ~ VaccinationStatus +
    NewsConsumption_z + Concern_z + CRT_score_z +
    StatementSequence_z +
    PoliticalOrientation + EconomicOrientation + Income_z + Religiosity + EthnicityBinary +
    education_z + Age_z + GenderBinary + (1 | user_id),
  data = processed_data %>%
    dplyr::filter(
      PoliticalOrientation != 3, GenderBinary != -1,
      fake_news_generation_source == 1
    )
)

# summary(PerceivedVeracity_linear_AI)

PerceivedVeracity_linear_Hum <- lmer(
  PerceivedVeracity_z ~ VaccinationStatus +
    NewsConsumption_z + Concern_z + CRT_score_z +
    StatementSequence_z +
    PoliticalOrientation + EconomicOrientation + Income_z + Religiosity + EthnicityBinary +
    education_z + Age_z + GenderBinary + (1 | user_id),
  data = processed_data %>%
    dplyr::filter(
      PoliticalOrientation != 3, GenderBinary != -1,
      fake_news_generation_source == 0
    )
)

# summary(PerceivedVeracity_linear_Hum)
```














```{r}
# pdf("Veracity_reg.pdf", width=11, height=7)

dwplot(list(PerceivedVeracity_linear_Hum, PerceivedVeracity_linear_AI), effects = "fixed") %>%
  relabel_predictors(
    c(
      vaccination1 = "VaccinationStatus",
      Concern_z = "Concern",
      NewsConsumption_z = "NewsConsumption",
      CRT_score_z = "CRT",
      Age_z = "Age",
      gender_binary1 = "Gender",
      PoliticalOrientation1 = "PoliticalOrientationly moderate - PoliticalOrientationly left",
      PoliticalOrientation2 = "PoliticalOrientationly right - PoliticalOrientationly left",
      EconomicOrientation1 = "Economic liberal - Economic strongly liberal",
      EconomicOrientation2 = "Economic moderate - Economic strongly liberal",
      EconomicOrientation3 = "Economic conservative - Economic strongly liberal",
      EconomicOrientation4 = "Economic strongly conservative- Economic strongly liberal",
      education_z = "EducationYears",
      religious1 = "Not religous - Religous",
      religious2 = "Atheist - Religous",
      Income_z = "Income",
      ethnicity_binary1 = "Ethnicity",
      StatementSequence_z = "StatementSequence"
    )
  ) +
  theme_bw() +
  theme(legend.position = c(0.71, 0.88), legend.background = element_rect(fill = "transparent", colour = "transparent"), text = element_text(size = 14), axis.text = element_text(size = 6),legend.text=element_text(size=6)) +
  geom_vline(
    xintercept = 0,
    colour = "grey60",
    linetype = 2
  ) +
  xlab("Coefficient Estimate") +
  scale_color_manual(
    name = "",
    labels = c("Human-generated fake news", "AI-generated fake news"),
    values = c("Model 1" = "#000666", "Model 2" = "#990000")
  )

# dev.off()
```






```{r,echo=FALSE}
share_linear_with_sequence_id <- lmer(
  WillingnessToShare ~ fake_news_generation_source +
    (1 | user_id) + StatementSequence_z,
  data = processed_data %>%
    dplyr::filter(WillingnessToShare_z != "NA")
)

# summary(share_linear_with_sequence_id)



share_regression_linear <- lmer(
  WillingnessToShare ~ fake_news_generation_source + VaccinationStatus + NewsConsumption_z +
    CRT_score_z + Concern_z + StatementSequence_z +
    PoliticalOrientation + EconomicOrientation + Income_z + Religiosity +
    EthnicityBinary + education_z + Age_z + GenderBinary + (1 | user_id),
  data = processed_data %>%
    dplyr::filter(WillingnessToShare_z != "NA", PoliticalOrientation != 3, GenderBinary != -1)
)

# summary(share_regression_linear)

# vif(share_regression_linear)


share_regression_linear_human <- lmer(
  WillingnessToShare ~ VaccinationStatus + NewsConsumption_z +
    CRT_score_z + Concern_z + StatementSequence_z +
    PoliticalOrientation + EconomicOrientation + Income_z + Religiosity +
    EthnicityBinary + education_z + Age_z + GenderBinary + (1 | user_id),
  data = processed_data %>%
    dplyr::filter(
      WillingnessToShare_z != "NA", fake_news_generation_source == 0,
      PoliticalOrientation != 3, GenderBinary != -1
    )
)
# summary(share_regression_linear_human)



share_regression_linear_AI <- lmer(
  WillingnessToShare ~ VaccinationStatus + NewsConsumption_z +
    CRT_score_z + Concern_z + StatementSequence_z +
    PoliticalOrientation + EconomicOrientation + Income_z + Religiosity +
    EthnicityBinary + education_z + Age_z + GenderBinary + (1 | user_id),
  data = processed_data %>%
    dplyr::filter(
      WillingnessToShare_z != "NA", fake_news_generation_source == 1,
      PoliticalOrientation != 3, GenderBinary != -1
    )
)
# summary(share_regression_linear_AI)
```


```{r}
# pdf("Share_reg.pdf", width=11, height=7)

dwplot(list(share_regression_linear_human, share_regression_linear_AI), effects = "fixed") %>%
  relabel_predictors(
    c(
      vaccination1 = "VaccinationStatus",
      Concern_z = "Concern",
      NewsConsumption_z = "NewsConsumption",
      CRT_score_z = "CRT",
      Age_z = "Age",
      gender_binary1 = "Gender",
      PoliticalOrientation1 = "PoliticalOrientationly moderate - PoliticalOrientationly left",
      PoliticalOrientation2 = "PoliticalOrientationly right - PoliticalOrientationly left",
      EconomicOrientation1 = "Economic liberal - Economic strongly liberal",
      EconomicOrientation2 = "Economic moderate - Economic strongly liberal",
      EconomicOrientation3 = "Economic conservative - Economic strongly liberal",
      EconomicOrientation4 = "Economic strongly conservative- Economic strongly liberal",
      education_z = "EducationYears",
      religious1 = "Not religous - Religous",
      religious2 = "Atheist - Religous",
      Income_z = "Income",
      ethnicity_binary1 = "Ethnicity",
      StatementSequence_z = "StatementSequence"
    )
  ) +

  theme_bw() +
  theme(legend.position = c(0.71, 0.63), legend.background = element_rect(fill = "transparent", colour = "transparent"), text = element_text(size = 14), axis.text = element_text(size = 6),legend.text=element_text(size=6)) +
  geom_vline(
    xintercept = 0,
    colour = "grey60",
    linetype = 2
  ) +
  xlab("Coefficient Estimate") +
  scale_color_manual(
    name = "",
    labels = c("Human-generated fake news", "AI-generated fake news"),
    values = c("Model 1" = "#000666", "Model 2" = "#990000")
  )


# dev.off()
```
# Robustness Check

Check for the source of the human-generated fake news (Snopes vs Politifact):

First figure for the percieved veracity and second figure for willingness to share.

```{r,echo=FALSE}
# summary(PerceivedVeracity_linear_Hum)

PerceivedVeracity_linear_snopes <- lmer(
  PerceivedVeracity_z ~ VaccinationStatus +
    NewsConsumption_z + Concern_z + CRT_score_z +
    StatementSequence_z +
    PoliticalOrientation + EconomicOrientation + Income_z + Religiosity + EthnicityBinary +
    education_z + Age_z + GenderBinary + (1 | user_id),
  data = processed_data %>%
    dplyr::filter(
      PoliticalOrientation != 3, GenderBinary != -1,
      statement_source == 0
    )
)

# summary(PerceivedVeracity_linear_snopes)

# vif(PerceivedVeracity_linear_snopes)

PerceivedVeracity_linear_politifacts <- lmer(
  PerceivedVeracity_z ~ VaccinationStatus +
    NewsConsumption_z + Concern_z + CRT_score_z +
    StatementSequence_z +
    PoliticalOrientation + EconomicOrientation + Income_z + Religiosity + EthnicityBinary +
    education_z + Age_z + GenderBinary + (1 | user_id),
  data = processed_data %>%
    dplyr::filter(
      PoliticalOrientation != 3, GenderBinary != -1,
      statement_source == 1
    )
)

# summary(PerceivedVeracity_linear_politifacts)
```
```{r}
dwplot(list(PerceivedVeracity_linear_Hum, PerceivedVeracity_linear_snopes, PerceivedVeracity_linear_politifacts), effects = "fixed") %>%
  relabel_predictors(
    c(
      vaccination1 = "VaccinationStatus",
      Concern_z = "Concern",
      NewsConsumption_z = "NewsConsumption",
      CRT_score_z = "CRT",
      Age_z = "Age",
      gender_binary1 = "Gender",
      PoliticalOrientation1 = "PoliticalOrientationly moderate - PoliticalOrientationly left",
      PoliticalOrientation2 = "PoliticalOrientationly right - PoliticalOrientationly left",
      EconomicOrientation1 = "Economic liberal - Economic strongly liberal",
      EconomicOrientation2 = "Economic moderate - Economic strongly liberal",
      EconomicOrientation3 = "Economic conservative - Economic strongly liberal",
      EconomicOrientation4 = "Economic strongly conservative- Economic strongly liberal",
      education_z = "EducationYears",
      religious1 = "Not religous - Religous",
      religious2 = "Atheist - Religous",
      Income_z = "Income",
      ethnicity_binary1 = "Ethnicity",
      StatementSequence_z = "StatementSequence"
    )
  ) +
  theme_bw() +
  theme(legend.position = c(0.71, 0.38), legend.background = element_rect(fill = "transparent", colour = "transparent"), text = element_text(size = 14), axis.text = element_text(size = 6),legend.text=element_text(size=6)) +
  geom_vline(
    xintercept = 0,
    colour = "grey60",
    linetype = 2
  ) +
  xlab("Coefficient Estimate") +
  scale_color_manual(
    name = "",
    labels = c("Human-generated fake news", "Snopes fake news", "Politifacts dake news"),
    values = c("Model 1" = "#000666", "Model 2" = "orange", "Model 3" = "green")
  )
```
```{r,echo=FALSE}
# summary(share_regression_linear_human)

share_linear_snopes <- lmer(
  WillingnessToShare ~ VaccinationStatus + NewsConsumption_z +
    CRT_score_z + Concern_z + StatementSequence_z +
    PoliticalOrientation + EconomicOrientation + Income_z + Religiosity +
    EthnicityBinary + education_z + Age_z + GenderBinary + (1 | user_id),
  data = processed_data %>%
    dplyr::filter(
      WillingnessToShare_z != "NA", statement_source == 0,
      PoliticalOrientation != 3, GenderBinary != -1
    )
)

# summary(PerceivedVeracity_linear_snopes)



share_linear_politifacts <- lmer(
  WillingnessToShare ~ VaccinationStatus + NewsConsumption_z +
    CRT_score_z + Concern_z + StatementSequence_z +
    PoliticalOrientation + EconomicOrientation + Income_z + Religiosity +
    EthnicityBinary + education_z + Age_z + GenderBinary + (1 | user_id),
  data = processed_data %>%
    dplyr::filter(
      WillingnessToShare_z != "NA", statement_source == 1,
      PoliticalOrientation != 3, GenderBinary != -1
    )
)

# summary(share_linear_politifacts)
```

```{r}
dwplot(list(share_regression_linear_human, share_linear_snopes, share_linear_politifacts), effects = "fixed") %>%
  relabel_predictors(
    c(
      vaccination1 = "VaccinationStatus",
      Concern_z = "Concern",
      NewsConsumption_z = "NewsConsumption",
      CRT_score_z = "CRT",
      Age_z = "Age",
      gender_binary1 = "Gender",
      PoliticalOrientation1 = "PoliticalOrientationly moderate - PoliticalOrientationly left",
      PoliticalOrientation2 = "PoliticalOrientationly right - PoliticalOrientationly left",
      EconomicOrientation1 = "Economic liberal - Economic strongly liberal",
      EconomicOrientation2 = "Economic moderate - Economic strongly liberal",
      EconomicOrientation3 = "Economic conservative - Economic strongly liberal",
      EconomicOrientation4 = "Economic strongly conservative- Economic strongly liberal",
      education_z = "EducationYears",
      religious1 = "Not religous - Religous",
      religious2 = "Atheist - Religous",
      Income_z = "Income",
      ethnicity_binary1 = "Ethnicity",
      StatementSequence_z = "StatementSequence"
    )
  ) +
  theme_bw() +
  theme(legend.position = c(0.71, 0.38), legend.background = element_rect(fill = "transparent", colour = "transparent"), text = element_text(size = 14), axis.text = element_text(size = 6),legend.text=element_text(size=6)) +
  geom_vline(
    xintercept = 0,
    colour = "grey60",
    linetype = 2
  ) +
  xlab("Coefficient Estimate") +
  scale_color_manual(
    name = "",
    labels = c("Human-generated fake news", "Snopes fake news", "Politifacts dake news"),
    values = c("Model 1" = "#000666", "Model 2" = "orange", "Model 3" = "green")
  )
```

Check the roubstness between using SocialOrientation and EcnomicOrientation: 
```{r,echo=FALSE}
# summary(PerceivedVeracity_linear)

PerceivedVeracity_linear_SocialOrientation <- lmer(
  PerceivedVeracity_z ~ fake_news_generation_source + VaccinationStatus +
    NewsConsumption_z + Concern_z + CRT_score_z +
    StatementSequence_z +
    PoliticalOrientation + SocialOrientation + Income_z + Religiosity + EthnicityBinary +
    education_z + Age_z + GenderBinary + (1 | user_id),
  data = processed_data %>% dplyr::filter(
    PoliticalOrientation != 3,
    GenderBinary != -1
  )
)
# summary(PerceivedVeracity_linear_SocialOrientation)
```



```{r}
dwplot(list(PerceivedVeracity_linear, PerceivedVeracity_linear_SocialOrientation), effects = "fixed") %>%
  relabel_predictors(
    c(
      vaccination1 = "VaccinationStatus",
      Concern_z = "Concern",
      NewsConsumption_z = "NewsConsumption",
      CRT_score_z = "CRT",
      Age_z = "Age",
      gender_binary1 = "Gender",
      PoliticalOrientation1 = "PoliticalOrientationly moderate - PoliticalOrientationly left",
      PoliticalOrientation2 = "PoliticalOrientationly right - PoliticalOrientationly left",
      EconomicOrientation1 = "Economic liberal - Economic strongly liberal",
      EconomicOrientation2 = "Economic moderate - Economic strongly liberal",
      EconomicOrientation3 = "Economic conservative - Economic strongly liberal",
      EconomicOrientation4 = "Economic strongly conservative- Economic strongly liberal",
      education_z = "EducationYears",
      religious1 = "Not religous - Religous",
      religious2 = "Atheist - Religous",
      Income_z = "Income",
      ethnicity_binary1 = "Ethnicity",
      StatementSequence_z = "StatementSequence"
    )
  ) +
  theme_bw() +
  theme(legend.position = c(0.71, 0.38), legend.background = element_rect(fill = "transparent", colour = "transparent"), text = element_text(size = 14), axis.text = element_text(size = 6),legend.text=element_text(size=6)) +
  geom_vline(
    xintercept = 0,
    colour = "grey60",
    linetype = 2
  ) +
  xlab("Coefficient Estimate") +
  scale_color_manual(
    name = "",
    labels = c("Percieved veracity mixed-effect linear with EconomicOrientation", "Percieved veracity mixed-effect linear with SocialOrientation"),
    values = c("Model 1" = "orange", "Model 2" = "green")
  )
```
```{r,echo=FALSE}
# summary(PerceivedVeracity_linear)

PerceivedVeracity_linear_plus_respond_time <- lmer(
  PerceivedVeracity_z ~ fake_news_generation_source + VaccinationStatus +
    NewsConsumption_z + Concern_z + CRT_score_z +
    StatementSequence_z +
    PoliticalOrientation + EconomicOrientation + Income_z + Religiosity + EthnicityBinary +
    education_z + Age_z + GenderBinary + Time_to_respond_z +
    (1 | user_id),
  data = processed_data %>% dplyr::filter(
    PoliticalOrientation != 3,
    GenderBinary != -1
  )
)
# summary(PerceivedVeracity_linear_plus_respond_time)
```
```{r}
dwplot(list(PerceivedVeracity_linear, PerceivedVeracity_linear_plus_respond_time), effects = "fixed") %>%
  relabel_predictors(
    c(
      vaccination1 = "VaccinationStatus",
      Concern_z = "Concern",
      NewsConsumption_z = "NewsConsumption",
      CRT_score_z = "CRT",
      Age_z = "Age",
      gender_binary1 = "Gender",
      PoliticalOrientation1 = "PoliticalOrientationly moderate - PoliticalOrientationly left",
      PoliticalOrientation2 = "PoliticalOrientationly right - PoliticalOrientationly left",
      EconomicOrientation1 = "Economic liberal - Economic strongly liberal",
      EconomicOrientation2 = "Economic moderate - Economic strongly liberal",
      EconomicOrientation3 = "Economic conservative - Economic strongly liberal",
      EconomicOrientation4 = "Economic strongly conservative- Economic strongly liberal",
      education_z = "EducationYears",
      religious1 = "Not religous - Religous",
      religious2 = "Atheist - Religous",
      Income_z = "Income",
      ethnicity_binary1 = "Ethnicity",
      StatementSequence_z = "StatementSequence",
      Time_to_respond_z = "Time to respond"
    )
  ) +
  theme_bw() +
  theme(legend.position = c(0.71, 0.38), legend.background = element_rect(fill = "transparent", colour = "transparent"), text = element_text(size = 14), axis.text = element_text(size = 6),legend.text=element_text(size=5)) +
  geom_vline(
    xintercept = 0,
    colour = "grey60",
    linetype = 2
  ) +
  xlab("Coefficient Estimate") +
  scale_color_manual(
    name = "",
    labels = c("Percieved veracity mixed-effect linear", "Percieved veracity mixed-effect linear plus Time_to_respond"),
    values = c("Model 1" = "orange", "Model 2" = "green")
  )
```

Check between using robust standard error and mixed-effect regression: 
```{r,echo=FALSE}
PerceivedVeracity_linear_roubst <- lm(
  PerceivedVeracity_z ~ fake_news_generation_source + VaccinationStatus +
    NewsConsumption_z + Concern_z + CRT_score_z +
    StatementSequence_z +
    PoliticalOrientation + EconomicOrientation + Income_z + Religiosity + EthnicityBinary +
    education_z + Age_z + GenderBinary,
  data = processed_data %>% dplyr::filter(
    PoliticalOrientation != 3,
    GenderBinary != -1
  )
)
# summary(PerceivedVeracity_linear_roubst)

PerceivedVeracity_linear_roubst_clustered <- coeftest(PerceivedVeracity_linear_roubst,
  vcov = vcovCL,
  type = "HC1",
  cluster = ~user_id
)
```


```{r}
dwplot(list(PerceivedVeracity_linear, PerceivedVeracity_linear_roubst_clustered), effects = "fixed") %>%
  relabel_predictors(
    c(
      vaccination1 = "VaccinationStatus",
      Concern_z = "Concern",
      NewsConsumption_z = "NewsConsumption",
      CRT_score_z = "CRT",
      Age_z = "Age",
      gender_binary1 = "Gender",
      PoliticalOrientation1 = "PoliticalOrientationly moderate - PoliticalOrientationly left",
      PoliticalOrientation2 = "PoliticalOrientationly right - PoliticalOrientationly left",
      EconomicOrientation1 = "Economic liberal - Economic strongly liberal",
      EconomicOrientation2 = "Economic moderate - Economic strongly liberal",
      EconomicOrientation3 = "Economic conservative - Economic strongly liberal",
      EconomicOrientation4 = "Economic strongly conservative- Economic strongly liberal",
      education_z = "EducationYears",
      religious1 = "Not religous - Religous",
      religious2 = "Atheist - Religous",
      Income_z = "Income",
      ethnicity_binary1 = "Ethnicity",
      StatementSequence_z = "StatementSequence",
      Time_to_respond_z = "Time to respond"
    )
  ) +
  theme_bw() +
  theme(legend.position = c(0.71, 0.88), legend.background = element_rect(fill = "transparent", colour = "transparent"), text = element_text(size = 14), axis.text = element_text(size = 6),legend.text=element_text(size=8)) +
  geom_vline(
    xintercept = 0,
    colour = "grey60",
    linetype = 2
  ) +
  xlab("Coefficient Estimate") +
  scale_color_manual(
    name = "",
    labels = c("Percieved veracity mixed-effect linear", "Percieved. veracity roubst error"),
    values = c("Model 1" = "orange", "Model 2" = "green")
  )
```

Check the Ordinal regression for percieved veracity: 

```{r, echo = FALSE}
PerceivedVeracity_ordinal <- clmm(
  PerceivedVeracity ~ fake_news_generation_source + VaccinationStatus +
    NewsConsumption_z + Concern_z + CRT_score_z +
    StatementSequence_z +
    PoliticalOrientation + Income_z + Religiosity + EthnicityBinary +
    education_z + Age_z + (1 | user_id),
  data = processed_data %>% dplyr::filter(PoliticalOrientation != 3) %>%
    mutate(PerceivedVeracity = as.factor(PerceivedVeracity))
)
summary(PerceivedVeracity_ordinal)
```

```{r,echo=FALSE}
PerceivedVeracity_linear_AI_ordinal <- clmm(
  PerceivedVeracity ~ VaccinationStatus +
    PoliticalOrientation + NewsConsumption + CRT_score_z +
    StatementSequence_z + Income + Religiosity +
    EthnicityBinary + education_z + (1 | user_id),
  data = processed_data %>% mutate(PerceivedVeracity = as.factor(PerceivedVeracity)) %>% dplyr::filter(PoliticalOrientation != 3, fake_news_generation_source == 1)
)

# summary(PerceivedVeracity_linear_AI_ordinal)
```

```{r,echo=FALSE}
 PerceivedVeracity_linear_Hum_ordinal <- clmm(
                                 PerceivedVeracity ~ VaccinationStatus +
                                 PoliticalOrientation + NewsConsumption + CRT_score_z +
                                 StatementSequence_z + Income + Religiosity +
                                EthnicityBinary + education_z + (1 | user_id),
                                 data = processed_data %>% mutate(PerceivedVeracity = as.factor(PerceivedVeracity)) %>% dplyr::filter(PoliticalOrientation != 3, fake_news_generation_source == 0)
                                  )

# summary(PerceivedVeracity_linear_Hum_ordinal)
```

Check the logistic regression for Willingness to share:

```{r,echo=FALSE}
shareRegresssion <- glmer(
  WillingnessToShare_fac ~ fake_news_generation_source +
    VaccinationStatus + NewsConsumption_z +
    CRT_score_z + Concern_z + StatementSequence_z +
    PoliticalOrientation + EconomicOrientation + Income_z + Religiosity +
    EthnicityBinary + education_z + Age_z + GenderBinary + (1 | user_id),
  family = binomial(link = "logit"),
  data = processed_data %>%
    dplyr::filter(
      WillingnessToShare_z != "NA",
      PoliticalOrientation != 3, GenderBinary != -1
    ), nAGQ = 0
)

# summary(shareRegresssion)
```
